Flexible Scientific Data Management for Plant Phenomics Research

### 2013-03-11 s4biodiv2013/PODD-S4BIODIV-Submission.tex
reduction of detail about the BagIt to DAP process

Currently, one bag is equivalent to a single batch scanned on the
PlantScan\textsuperscript{\texttrademark}
local software system, which usually means the same kind of plant with different
genotypes scanned under one  experiment configuration profile.  However the
naming, content and amount of data in a bag are flexible and depend upon the
intention of the bag. For example, multiple batches can be packed into one bag
when the batches come from one plant’s scans at different time points. The
multi-threaded BagIt tool is called on the ASC HPC host to create a bag that is
then compressed into a single file containing a top-level data folder, a
manifest file that contains checksums for every data file, and tag files that
contain the metadata description of the bag just packed.

The metadata required for a DAP publication is created and the bag transferred
to the DAP staging area via SFTP (SSH File Transfer Protocol). After publication
of the DAP collection, the data from PlantScan\textsuperscript{\texttrademark}
for the given project becomes
discoverable via DAP. In addition, experiment reports, published papers, and
sensor configurations can either be made accessible via a DAP collection's
``related materials'' links, other metadata fields, or within the collection's
data (e.g. bag).

>>>>

Currently, one bag is equivalent to a single batch scanned on the
PlantScan\textsuperscript{\texttrademark}
local software system, which usually means the same kind of plant with different
genotypes scanned under one  experiment configuration profile.  
% However the
% naming, content and amount of data in a bag are flexible and depend upon the
% intention of the bag. For example, multiple batches can be packed into one bag
% when the batches come from one plant’s scans at different time points. The
% multi-threaded BagIt tool is called on the ASC HPC host to create a bag that is
% then compressed into a single file containing a top-level data folder, a
% manifest file that contains checksums for every data file, and tag files that
% contain the metadata description of the bag just packed. 
The metadata required for a DAP publication is created and the bag transferred
to the DAP staging area via SFTP (SSH File Transfer Protocol). After publication
of the DAP collection, the data from PlantScan\textsuperscript{\texttrademark}
for the given project becomes
discoverable via DAP. In addition, experiment reports, published papers, and
sensor configurations can either be made accessible via a DAP collection's
``related materials'' links, other metadata fields, or within the collection's
data (e.g. bag).
